Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-01-06 WSSSPE3/report/WSSSPE3_review.tex

%
\thanks{{}$^{(1)}$ Computation Institute, 
University of Chicago \& Argonne National Laboratory, Chicago, IL, USA; d.katz@ieee.org}
%
\thanks{{}$^{(2)}$ School of Mechanical, Industrial, and Manufacturing Engineering, 
Oregon State University, Corvallis, OR, USA; kyle.niemeyer@oregonstate.edu}
%
\thanks{{}$^{(3)}$ NORC at the University of Chicago and Illinois Institute of Technology, Chicago, IL, USA; sctchoi@uchicago.edu}
%
\thanks{{}$^{(4)}$ Research Software Development Group, University College London, UK; j.hetherington@ucl.ac.uk}
%
\thanks{{}$^{(5)}$ Center for Computation \& Technology, Louisiana State University, Baton Rouge, LA, USA; \{knarf,sbrandt\}@cct.lsu.edu}
%
\thanks{{}$^{(6)}$ Lawrence Berkeley National Laboratory, Berkeley, USA; dkgunter@lbl.gov}
%
\thanks{{}$^{(7)}$ RENCI, Chapel Hill, NC, USA; rayi@renci.org}
%
\thanks{{}$^{(8)}$ University of California, San Diego, CA, USA; mmiller@sdsc.edu}
%
\thanks{{}$^{(9)}$ unit, institution, city, country; email}
%
\thanks{{}$^{(10)}$ New Zealand eScience Infrastructure (NeSI), University of Auckland, Auckland, NZ; nick.jones@nesi.org.nz}
%
\thanks{{}$^{(11)}$ unit, institution, city, country; email}
%
\thanks{{}$^{(12)}$ National Center for Supercomputing Applications, University of Illinois at Urbana-Champaign, Urbana, IL, USA; gdallen@illinois.edu}
%
\thanks{{}$^{(13)}$ School of Computing and Engineering, University of Huddersfield, Huddersfield, UK; C.Venters@hud.ac.uk}
%
\thanks{{}$^{(14)}$ unit, institution, city, country; email}
%
\thanks{{}$^{(15)}$  University of California, Davis, CA, USA; ljhwang@ucdavis.edu}
%
\thanks{{}$^{(16)}$ unit, institution, city, country; email}
%
\thanks{{}$^{(17)}$ unit, institution, city, country; email}
%
\thanks{{}$^{(18)}$ Department of Astrophysical Sciences, 
Princeton University, Princeton, NJ, USA; mdevalbo@astro.princeton.edu}
%

@@

WSSSPE3 began with a keynote speech delivered by Professor Matthew Turk from the
Department of Astronomy, University of Illinois, titled \emph{Why Sustain
Scientific Software?}. Turk is a prolific scientific software practitioner and
has extensive experiences working on large collaborative projects employing
modern computing tools. He also co-organizes and champions WSSSPE events.

>>>>

%
\thanks{{}$^{(1)}$ Computation Institute, 
University of Chicago \& Argonne National Laboratory, Chicago, IL, USA; d.katz@ieee.org}
%
\thanks{{}$^{(2)}$ School of Mechanical, Industrial, and Manufacturing Engineering, 
Oregon State University, Corvallis, OR, USA; kyle.niemeyer@oregonstate.edu}
%
\thanks{{}$^{(3)}$ NORC at the University of Chicago and Illinois Institute of Technology, Chicago, IL, USA; sctchoi@uchicago.edu}
%
\thanks{{}$^{(4)}$ Research Software Development Group, University College London, UK; j.hetherington@ucl.ac.uk}
%
\thanks{{}$^{(5)}$ Center for Computation \& Technology, Louisiana State University, Baton Rouge, LA, USA; \{knarf,sbrandt\}@cct.lsu.edu}
%
\thanks{{}$^{(6)}$ Lawrence Berkeley National Laboratory, Berkeley, USA; dkgunter@lbl.gov}
%
\thanks{{}$^{(7)}$ RENCI, Chapel Hill, NC, USA; rayi@renci.org}
%
\thanks{{}$^{(8)}$ University of California, San Diego, CA, USA; mmiller@sdsc.edu}
%
\thanks{{}$^{(9)}$ Center for Research Computing, University of Notre Dame, Notre Dame, IN, USA; sandra.gesing@nd.edu}
%
\thanks{{}$^{(10)}$ New Zealand eScience Infrastructure (NeSI), University of Auckland, Auckland, NZ; nick.jones@nesi.org.nz}
%
\thanks{{}$^{(11)}$ unit, institution, city, country; email}
%
\thanks{{}$^{(12)}$ National Center for Supercomputing Applications, University of Illinois at Urbana-Champaign, Urbana, IL, USA; gdallen@illinois.edu}
%
\thanks{{}$^{(13)}$ School of Computing and Engineering, University of Huddersfield, Huddersfield, UK; C.Venters@hud.ac.uk}
%
\thanks{{}$^{(14)}$ unit, institution, city, country; email}
%
\thanks{{}$^{(15)}$  University of California, Davis, CA, USA; ljhwang@ucdavis.edu}
%
\thanks{{}$^{(16)}$ unit, institution, city, country; email}
%
\thanks{{}$^{(17)}$ unit, institution, city, country; email}
%
\thanks{{}$^{(18)}$ Department of Astrophysical Sciences, 
Princeton University, Princeton, NJ, USA; mdevalbo@astro.princeton.edu}
%

@@

WSSSPE3 began with a keynote speech delivered by Professor Matthew Turk from the
Department of Astronomy, University of Illinois, titled \emph{Why Sustain
Scientific Software?}. Turk is a prolific scientific software practitioner and
has extensive experiences working on large collaborative projects employing
modern computing tools \cite{2011ApJS..192....9T}. He also co-organizes and
champions WSSSPE events.
